---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# indiamapdata

<!-- badges: start -->

<!-- badges: end -->

The goal of indiamapdata is to serve as a container package for the maps
data used in indiamap package. This data has been separated to keep the
size of the indiamap package manageable and facilitate easier
maintenance, while enabling more frequent updates to the Indian map data
frame without relying on indiamap package updates.

## Map data

The geojson files are stored in the data-raw/geojson_files folder. These
files were read using the `sf` package, joined with state_abbr excel
files, and saved as gpkg files in the inst/extdata folder. Centroids for
the state data were calculated using the `st_centroid` function. The
district centroids could not be calculated due to an overlap in the
data.

## Installation

You can install the development version of indiamapdata from
[GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("shubhamdutta26/indiamapdata")
```

## Usage

To begin using `indiamapdata`, import the package using the `library`
command:

```{r usage}
library(indiamapdata)
```

## Acknowledgments

I would like to thank [datta07](https://github.com/datta07) for the geojson files.
