---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# indiamapdata

<!-- badges: start -->

<!-- badges: end -->

The goal of indiamapdata is to serve as a container package for the maps
data used in indiamap package. This data has been separated to keep the
size of the indiamap package manageable and facilitate easier maintenance, 
while enabling more frequent updates to the Indian map data frame without 
relying on indiamap package updates.

## Map data

The geojson files are stored in the data-raw/geojson_files folder. These files 
were read and appropriately modified using the `create_india_map` function
and saved as gpkg files in the inst/extdata folder. The centroids were also 
calculated using the `compute_centroids` function.

## Installation

You can install the development version of indiamapdata from
[GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("shubhamdutta26/indiamapdata")
```

## Usage

To begin using `indiamapdata`, import the package using the `library`
command:

```{r usage}
library(indiamapdata)
```

## Acknowledgments

I would like to thank [pdil](https://github.com/pdil) since I have used his 
`usmap` package to write most of this package. I would like to thank [datta07](https://github.com/datta07) for the geojson files.

